%
% ---- Bibliography ----
%
\clearpage

\begin{thebibliography}{}
%
\bibitem[1]{stellman}
A. Stellman, and J. Greene.:
Applied Software Project Management.
OREILLY, (2005)

\bibitem[2]{chang}
C. K. Chang, H. Jiang, Y. Di, D. Zhu, and Y. Ge.:
Time-line Based Model for Software Project 
Scheduling with Genetic Algorithms.
Information and Software Technology, 1142-1154 (2008)

\bibitem[3]{alba}
E. Alba, and C. J. Francisco.:
Software Project Management with GA.
Information Sciences, 2380-2401 (2007)

\bibitem[4]{ren}
J. Ren, M. Harman, and M. D. Penta.:
Cooperative Co-evolutionary Optimization of Software 
Project Staff Assignments and Job Scheduling.
Lecture Notes in Computer Science, Springer Berlin Heidelberg, 495-519 (2011)

\bibitem[6]{pentico}
D. W. Pentico.:
Assignment Problems: A Golden Anniversary Survey.
European Journal of Operational Research, 774-793 (2007)

\bibitem[5]{penta}
M. D. Penta, M. Harman, and G. Antoniol.:
The Use of Search-based Optimization Techniques to 
Schedule and Staff Software Projects: An Approach and an Empirical Study. 
Software: Practice and Experience, 495-519 (2011)

\bibitem[7]{pospichal}
P. Pospichal, J. Jaros, and J.:
Schwarz. Parallel Genetic Algorithm on the CUDA Architecture.
Lecture Notes Computation Science, 442-451 (2010)

% \bibitem[8]{qu}
% 曲婉玲, 刘田.:
% 算法设计与分析.
% 北京:清华大学出版社, 205-207 (2011)

\bibitem[9]{stylianou}
C. Stylianou, S. Gerasimou, and A. S. Andreou.:
A Novel Prototype Tool for Intelligent Software 
Project Scheduling and Staffing Enhanced with Personality Factors.
IEEE 24th International Conference on Tools with Artificial Intelligence. 277-284 (2012)

\bibitem[10]{samanta}
S. Samanta.:
Genetic Algorithm: An Approach for Optimization (Using MATLAB). 
International Journal of Latest Trends in Engineering and Technology, 261-267 (2014)

\bibitem[11]{holland}
J. H. Holland.:
Adaptation in Natural and Artificial Systems: an Introductory 
Analysis with Applications to Biology, Control, and Artificial Intelligence.
U Michigan Press, (1975)

\bibitem[12]{harman}
M. Harman, P. McMinn, J. T. D. Souza, and S. Yoo.:
Search Based Software Engineering: Techniques, Taxonomy, Tutorial.
Empirical software engineering and verification, 1-59 (2012)

\bibitem[13]{deb}
K. Deb, A. Pratap, S. Agarwal, and T. Meyarivan.:
A Fast and Elitist Multiobjective Genetic Algorithm: NSGA-II.
IEEE Transactions on Evolutionary Computation, 182-197 (2002)

\bibitem[14]{vidal}
P. Vidal, and E. Alba.:
A Multi-GPU Implementation of a Cellular Genetic Algorithm.
2010 IEEE World Congress on Computational Intelligence, 1-7 (2010)

\bibitem[15]{sarro}
F. Sarro, F. Ferrucci, M. Harman, A. Manna and J. Ren.:
Adaptive Multi-objective Evolutionary Algorithms for Overtime Planning in Software Projects.
IEEE Transactions on Software Engineering, PP(99):1-1 (2017)

\bibitem[16]{zhang}
F. Zhang, Z. Li, B. Wang, M. Xiang, W. Hong.：
Hybrid general-purpose computation on GPU (GPGPU) and computer graphics synthetic aperture radar simulation for complex scenes.
International Journal of Physical Sciences, 1224-1234 (2012)

\bibitem[17]{li}
Z. Li, Y. Bian, R. Zhao, J. Cheng.：
A Fine-Grained Parallel Multi-objective Test Case Prioritization on GPU.
International Symposium on Search Based Software Engineering, 111-125 (2013)

\bibitem[18]{langdon2}
WB. Langdon，BYH. Lam, J. Petke，M. Harman.：
Improving CUDA DNA Analysis Software with Genetic Programming.
Conference on Genetic \& Evolutionary Computation, 1063-1070 (2015)

\bibitem[19]{langdon1}
WB. Langdon，BY. Lam，M. Modat，J. Petke，M. Harman.：
Genetic improvement of GPU software.
Genetic Programming and Evolvable Machines, 18(1):5-44 (2017)

\bibitem[20]{ren2}
Jian. Ran.：
Search Based Software Project Management.
University of London., 1-178 (2013)


% \bibitem[15]{kirk}
% D.B. Kirk, W. W. Hwu.:
% 大规模并行处理器编程实战（第二版）.
% 北京: 清华大学出版社, 1-31 (2013)




% ---------------------------------
% \bibitem[1980]{2clar:eke}
% Clarke, F., Ekeland, I.:
% Nonlinear oscillations and
% boundary-value problems for Hamiltonian systems.
% Arch. Rat. Mech. Anal. 78, 315--333 (1982)

% \bibitem[1981]{2clar:eke:2}
% Clarke, F., Ekeland, I.:
% Solutions p\'{e}riodiques, du
% p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
% Note CRAS Paris 287, 1013--1015 (1978)

% \bibitem[1982]{2mich:tar}
% Michalek, R., Tarantello, G.:
% Subharmonic solutions with prescribed minimal
% period for nonautonomous Hamiltonian systems.
% J. Diff. Eq. 72, 28--55 (1988)

% \bibitem[1983]{2tar}
% Tarantello, G.:
% Subharmonic solutions for Hamiltonian
% systems via a $\bbbz_{p}$ pseudoindex theory.
% Annali di Matematica Pura (to appear)

% \bibitem[1985]{2rab}
% Rabinowitz, P.:
% On subharmonic solutions of a Hamiltonian system.
% Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}
\clearpage

% end of bibliography
