
\section{Introducition to Evolution Algorithm}
\subsection{Meta-heuristic Algorithms}
%
In the process of computer science development, the program algorithm design 
provides much power to advance the advancement of computer science and 
technology. We know that in solving the same kind of problem, the 
computational efficiency of different algorithms is completely different. 
Algorithm has become the soul of the computer to solve practical problems. In 
addition to the current algorithm that can be used to calculate a problem at 
a given time, a class of algorithms is found that no performance guarantee 
can be given theoretically at present, but in practice it is often possible 
to give the solution of the problem efficiently. This algorithm is called meta
-heuristic algorithm.   

Unlike the usual algorithmic algorithm, the meta-heuristic algorithm tries to 
provide one or more goals in a single calculation, and the corresponding 
optimal solution can be found in the run. The heuristic algorithm can often 
find a good solution, but there is no way to prove that it won’t get a worse 
solution, and even sometimes cannot find solution. The evolutionary algorithm 
used in this paper usually gives an approximate optimal answer within a given 
time, but there is usually no way to ensure that a sufficient solution is 
given at a given time.

In reality, there are some extreme cases in the process of implementing the 
heuristic algorithm, that is, some solutions of the meta-heuristic algorithms 
are difficult to find, or they cannot be found at all. The heuristic 
algorithm is often used to solve some Non-Deterministic Polynomial complete 
problems because the theoretical Non-Deterministic Polynomial complete 
problem is computationally large and cannot use some deterministic algorithms 
to find the optimal solution. However, the meta-heuristic algorithm can get a 
good answer in a reasonable time when dealing with such Non-Deterministic 
Polynomial complete problem, so the meta-heuristic algorithm is also a hot 
field of academic research.

The idea of the meta-heuristic algorithm has been around for a long time, and 
since its formation, the research on it has not been interrupted, and there 
are many ways to achieve it now. In recent decades, the research of meta-
heuristic algorithm has developed rapidly, and there have been many more 
mature and specific algorithms. In the 1970s, Professor Holland proposed 
genetic algorithm\cite{holland} (Genetic Algorithm). Genetic algorithm 
simulates the evolutionary method of biological population to find the 
optimal solution of some problems, which opens up a new round of research on 
meta - heuristic algorithm. In the 1980s, a number of new generation 
heuristic algorithms emerged, such as Simulated Annealing Algorithm, 
Artificial Neural Network, Tabu Search. Now, the relatively hot heuristic 
algorithms are Evolutionary Algorithm, Ant Algorithms, Genetic Quantum 
Algorithm. The research of meta-heuristic algorithms has been thinking about 
a new and highly developed\cite{harman}.

\subsection{Evolutionary Algorithm}
%
Evolutionary algorithm draws on Darwin's theory of evolution and Mendel's 
theory of genetic genetics. Its essence is an efficient global search 
algorithm that imitates the biological evolution of nature. It can 
automatically acquire and accumulate the knowledge of the huge search space 
in the process of searching for the optimal solution automatically, and adapt 
to controlling search process by itself. It can be directional to obtain the 
convergence of the better solution according to the natural law of the 
superior is better, the stronger the stronger\cite{deb}.
Figure 1 summarizes the basic process of the evolutionary algorithm. The core 
of the evolutionary algorithm is the design of the solution coding from and 
the fitness evaluation function. The evolutionary algorithm first code the 
form of the solution according to the different problem requirements, and 
then each individual in the population represents a solution to the problem. 
At the same time, for each problem, we also need to evaluate the fitness 
evaluation function of the solution. The fitness value of different solutions 
is used to measure the adaptability of an individual. Individuals with high 
adaptability are more likely to survive in the evolution of the population. 
The operation of the evolutionary algorithm has initialized population, 
crossover, mutation, selection. The initial population refers to the random 
generation of the first generation of population; the cross is a process of 
the individual hybridization between parents and the production of new 
offspring population; mutation is a process of the certain genes to be 
mutated in the individual, mutated individuals involved in population 
hybridization to maintain the species diversity of the population, and also 
will get some new solutions; choice is to choose each individual population, 
according to the natural law of the survival the fittest that is used to 
eliminate the inferior individual. The evolutionary algorithm finally obtains 
the optimal solution we want to by the evolution of the population.


