% !TEX root = ../paper.tex
% header
%

\title{Parallel Evolutionary Algorithm in Solving Single Objective Software Project Management Problem}
%Solving Project Management Problem with Parallel Evolutionary Algorithm}
%
\titlerunning{Project Management}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{ Jinghui Hu\inst{1} \and Xu Wang\inst{1} \and Jian Ren\inst{1} \and Chao Liu\inst{1}}
%
\authorrunning{Hu, Wang, Ren, Liu} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Jinghui Hu, Xu Wang, Jian Ren, Chao Liu}
%
\institute{School of Computer Science and Engineering, \\Beihang University, Beijing 100191, China\inst{1}
%\\
%\email{\{hujinghui, bhwangxu, renjian, liuchao\}@buaa.edu.cn}
\thanks{supported by the Technology Foundation Program (JSZL2014601B008) of the National Defense Technology Industry Ministry \textbf{NEED CHECK}}
}



\maketitle

\begin{abstract}
Software project management problem mainly includes resources allocation and work packages scheduling.
This paper presents an approach to Search Based Software Project Management based on paralleled implementation of evolutionary algorithm on GPU. 
Our approach aims to paralleled the genetic operators including: crossover, mutation and evaluation in the evolution process to achieve faster execution time for the optimization process.
To evaluate our approach, we conducted a ``proof of concept'' empirical study, using data from three real-world software projects. 
Both sequential and parallel version of a conventional single objective evolutionary algorithm are implemented. 
%The objective is to minimize the overall duration a software project, while satisfying the dependencies between work packages and constraints of resources allocation in the software project.
The sequential version application is based on common programming approach using C++ programming language, and the parallel version application is based on GPGPU programming approach using CUDA C++ API.
We redesign search based evolutionary algorithm to cater for our purpose of parallel programming on GPU.
Results indicate that even a relatively cheap graphic card (GeForce GTX 970) can speed up the optimization process significantly.
We believe that deploy parallel evolutionary algorithm based on GPU  may fit many applications for other software project management problems, since software projects often have complex inter-related tasks and resource and are typically characterized by large scale problems that need to be paralleled to improve execution time.


\keywords{Software project management, Evolutionary algorithm, Parallel Optimization Problem}
\end{abstract}
