% !TEX root = ../paper.tex
%% chapter 6
%\vspace{-6mm}

%\vspace{-3mm}
\section{Related Works}
\vspace{-2mm}

In 1993, Chang et al.~\cite{chang} first proposed the project management problem. The view of
Chang is that software project management net(SPM-Net) can be used to
schedule tasks and manage the resources of software development.
In his article, Chang's project management problem is based on the simulative
data, the reason leading to this is the real industrial data of software
project management is very scanty. In 2007, Alba and Chicano~\cite{alba} optimized the
search algorithms for project management, and solve the project management
problem using genetic algorithm. Their goal is using a search-based approach
to reduce the final completion duration of a project. In 2009, Ren et al.~\cite{ren} first
applied co-evolutionary algorithms to solve project management problem.
Recently, Sarro et al.~\cite{sarro} proposed a a multi-objective decision support approach to help
balance project risks and duration against overtime, so that software
engineers can better plan overtime.
At present, the search space of the work package based on the project
management is more and more huge, the sequential algorithm is not so
effective to solve such problems. Thus, finding a parallel algorithm has
become a hot topic on research~\cite{pentico}.


In recent years, search-based project management problem has become an
important branch of search-based software engineering, and has become a new
field of research. At the same time, the number of papers related to search-
based project management problem is also rising, which makes many researchers
willing to engage in search-based project management problem, so in turn
provides a new platform for practice and innovation of the search-based
project management problem~\cite{penta}.
In 2011, Thomas~\cite{thomas} proposed an approach to describe software project problems
with a set of multi-objective criteria for portfolio managers using the COCOMO II model and
introduce a multi-objective evolutionary approach.
In 2014, Samanta~\cite{samanta} gone through a very brief idea on Genetic Algorithm and implemented the algorithm using MATLAB.
The search-based algorithm is a compute-intensive method, which means the
computer's CPU will be used usually consumed a lot. Therefore, the traditional
sequential computing model cannot meet the requirement of increasing calculation
speed. In 2007, Alba and Chicano~\cite{pospichal} began using search-based methods to improve the
optimal solution of problems, and for the first time using a parallel code model to test the efficiency of search-based methods.
In 2013, Jing~\cite{jing} began solving software project scheduling problems with ant colony optimization.
In recent years, more search-based software engineering methods (such as simulated
annealing, climbing algorithms, evolutionary algorithms, tabu search, etc.) have
been used to solve project management problem, and these methods are usually
able to get good convergence solution on project management problem.

As the development of the algorithm, how to speed up the calculation of the algorithm
has become a hot spot in academic community.
In 2012, Zhang et al.~\cite{zhang} apply GPGPU to
simulation for complex scenes and later on they proposed a GPU-based parallel MOEAs~\cite{li}.
CUDA is a generic parallel computing architecture developed by NVIDIA, which can be used to improve the performance of GPGPU~\cite{langdon2} and also can be optimized by meta-heuristic algorithms~\cite{langdon1,langdon3}.
In 2014, Jianmei~\cite{jianmei} proposed five novel parallel algorithms for solving 
multi-objective combinatorial optimization problems exactly and efficient.
Compared to our work, those algorithms are different in solved questions, but there is the same
thought of parallelization to gain the faster speed. They apply the algorithm to the case of
software-system designs and get great solution, which illustrate the great characteristic of
parallelization in the domain of software engineering.
In general, the parallel evolution algorithm can be implemented on the GPU platform using the CUDA~\cite{vidal}. With the development of the technology of parallelism, a general-purpose GPU(GPGPU) is used
to improve the speed of calculation in software engineering. 


%\textbf{THIS PARAGRAPH TALK TO TOOL, TO BE DELETED???}
Furthermore, a common project management tool which deal with
the mathematical models have not been implemented, so it is difficult to apply
the theory to the industrial project management process. In 2012, Stylianou~\cite{stylianou} and
Gerasimou first developed a tool for project management, which they named
IntelliSPM. The tool uses Matlab and Java programming language and
supports staffing arrangement and resource allocation optimization. In
their work, Stylianou uses the fitness function to dynamic calculate the
dependencies between work packages, so the real project's dependencies may be
broken during the calculation. So in current software engineering practice, the
tool supporting project management is still lacking.

